$jk$-means tests

### 2016-09-06 Rmd/unequalClustersTestSmallN.Rmd
sync

###1. Generate Data
Let's generate data from 2 clusters, each of size n

@@

mu0<- c(c(0.7,0.3), c(0.3,0.7))
mu<- matrix( 0,n*2,p)
mu[1:n,]<- rep(c(0.7,0.3),each=n)
mu[(n+1):(2*n),]<- rep(c(0.3,0.7),each=n)

sigma<-  sqrt(1.7661/n)

@@

computeMError<- function(jk, n){
  error<- numeric(batchN)
  for(b in 1:batchN){
    newOrder<- order(jk$mu[,1,b],decreasing = T)
    trueM<- rep( c(0,1)[newOrder], each=n)
    error[b]<- sum (jk$M[,b] != trueM) /2/n
  }
  error
}

@@

error12 <- computeMError(jk12,n)

mean(error12)
```

@@

error22 <- computeMError(jk22,n)

mean(error22)
```

@@

error22 <- computeMError(jk22,n)

mean(error22)
```

>>>>

###1. Generate Data
Let's generate data from 2 clusters, with size n/2, n/2*3

@@

mu0<- c(c(0.7,0.3), c(0.3,0.7))
mu<- matrix( 0,n*2,p)
mu[1:(n/2),]<- rep(c(0.7,0.3),each=(n/2))
mu[(n/2+1):(2*n),]<- rep(c(0.3,0.7),each=(n/2*3))

sigma<-  sqrt(1.7661/30)

@@

computeMError<- function(jk, n){
  error<- numeric(batchN)
  for(b in 1:batchN){
    newOrder<- order(jk$mu[,1,b],decreasing = T)
    tM0<- c(0,1)[newOrder]
    trueM<- c(rep(tM0[1],(n/2)),rep(tM0[2],(n/2*3)))
    error[b]<- sum (jk$M[,b] != trueM) /2/n
  }
  error
}

computeRMSE<- function(jk, mu0){
  rmse<- numeric(batchN)
  for(b in 1:batchN){
    newOrder<- order(jk$mu[,1,b],decreasing = T)

    muEst<-jk$mu[,,b][newOrder,]

    rmse[b]<- sqrt( mean((muEst - mu0)^2))
  }
  rmse
}

@@

error12 <- computeMError(jk12,n)
rmse12 <- computeRMSE(jk12, mu0)

mean(error12)
mean(rmse12)
```

@@

error22 <- computeMError(jk22,n)
rmse22 <- computeRMSE(jk22, mu0)

mean(error22)
mean(rmse22)
```

@@

error22 <- computeMError(jk22,n)
rmse22 <- computeRMSE(jk22, mu0)

mean(error22)
mean(rmse22)
